Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-09 paper/section-discussion.tex
Grammatical fixes to the discussion section

We have presented a general framework for algebraically indexed types
and instantiated it to yield novel type systems for geometry, logical
information flow and distance-indexed types. Our framework further
demonstrates the power of relational reasoning about typed
programs. From \thmref{thm:abstraction}, we have derived interesting
free theorems, type isomorphisms and non-definability results. We
conclude with some observations and suggestions for further work.

\paragraph{Further Applications and Extensions} We have covered
several applications of algebraically indexed types in this paper, but
there are undoubtedly many more. Geometry for dimensions greater than
two is an obvious candidate, as well as systems that are invariant
under different geometric groups (e.g.,~the Poincar\'{e} group for
relativity). Mathematical Physics is particularly rich in theories
that have some notion of invariance, and it will be exciting to pin
down the precise connections between these and type systems for which
analogues of Reynolds' abstraction theorem hold. Geometric theorem
proving is another possible application area. Harrison
\cite{harrison09without} comments on the pervasive useful of
invariance properties in this area. Programs in our framework
automatically satisfy invariance properties, removing the need for
ad-hoc proofs of these facts.

>>>>

We have presented a general framework for algebraically indexed types
and instantiated it to yield novel type systems for geometry, taint
tracking, logical information flow and distance-indexed types. Our
framework further demonstrates the power of relational reasoning about
typed programs. From \thmref{thm:abstraction}, we have derived
interesting free theorems, type isomorphisms and non-definability
results. We conclude with some observations and suggestions for
further work.

\paragraph{Further Applications and Extensions} We have covered
several applications of algebraically indexed types in this paper, but
there are undoubtedly many more. Geometry for dimensions greater than
two is an obvious candidate, as well as systems that are invariant
under different geometric groups (e.g.,~the Poincar\'{e} group for
relativity). Mathematical Physics is particularly rich in theories
that have some notion of invariance, and it will be exciting to pin
down the precise connections between these and type systems for which
analogues of Reynolds' abstraction theorem hold. Geometric theorem
proving is another possible application. Harrison
\cite{harrison09without} comments on the pervasive usefulness of
invariance properties in this area. Programs in our framework
automatically satisfy invariance properties, removing the need for
ad-hoc proofs of these facts.
